Groups and smooth geometry using LieGroups.jl

### 2025-11-01 paper/header.tex
second example
Fix metadata and giving the paper a careful read.

\author[1]{Ronny Bergmann}
\affil[1]{Department of Mathematical Sciences, Norwegian University of Science and Technology, Trondheim, Norway}

\keywords{Julia, Riemannian manifolds, Lie groups, Differential geometry}

\hypersetup{
pdftitle = {Groups and smooth geometry using LieGroups.jl},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Ronny Bergmann},
pdfkeywords = {Julia, Riemannian manifolds, Lie groups, Differential geometry},
}

>>>>

\author[1]{Ronny Bergmann}
\author[2]{Mateusz Baran}
\affil[1]{Department of Mathematical Sciences, Norwegian University of Science and Technology, Trondheim, Norway}
\affil[2]{AGH University of Science and Technology, Kraków, Poland}

\keywords{Riemannian manifolds, Lie groups, differential geometry, numerical analysis, scientific computing}

\hypersetup{
pdftitle = {Groups and smooth geometry using LieGroups.jl},
pdfsubject = {JuliaCon 2025 Proceedings},
pdfauthor = {Ronny Bergmann, Mateusz Baran},
pdfkeywords = {Riemannian manifolds, Lie groups, differential geometry, numerical analysis, scientific computing},
}
